What words ought to exist? \\ {\normalsize Coining with coinduction}

### 2011-03-12 trunk/wishlist/paper.tex
this almost works...

It basically makes sense to consider the probability of a whole word
to be the chance of simultaneously seeing each pair of letters in it,
which is just the product. So the word ``hel'' is $2/3$ (for {\bf
  \<h}) $\times$ 2/2 (for {\bf he}) $\times$ 4/4 (for {\bf el}) $\times$ 2/6 (for
{\bf l\>}), which is $0.222$. These are the most likely words overall (I
discuss how to generate such lists in Section~\ref{sec:coin}):

\vspace{0.2in}
\begin{tabular}{rl@{\quad}rl}
22.2\%  &  hel      &      2.5\%  &  helpfel  \\
11.1\%  &  helo     &      2.5\%  &  helafel  \\
 7.4\%  &  fel      &      1.9\%  &  fulo     \\
 3.7\%  &  hell     &      1.9\%  &  hello    \\
 3.7\%  &  felo     &      1.2\%  &  fell     \\
 3.7\%  &  ful      &      1.2\%  &  helafelo \\
\end{tabular}
\vspace{0.2in}

@@

The next step is to build a Markov chain for a list of real words and
see what results.

@@

@@

@@

sweeeeeeeeeeeeeeeeeeet with 19 {\it e}s.

>>>>

It basically makes sense to consider the probability of a whole word
to be the chance of simultaneously seeing each pair of letters in it,
which is just the product of all the probabilities. So the word
``hel'' is $2/3$ (for {\bf \<h}) $\times$ 2/2 (for {\bf he}) $\times$
4/4 (for {\bf el}) $\times$ 2/6 (for {\bf l\>}), which is $0.222$.
These are the most likely words overall (I discuss how to generate
such lists in Section~\ref{sec:coin}):

\vspace{0.2in}
\begin{tabular}{rl@{\quad\quad}rl}
22.2\%  &  hel      &      2.5\%  &  helpfel  \\
11.1\%  &  helo     &      2.5\%  &  helafel  \\
 7.4\%  &  fel      &      1.9\%  &  fulo     \\
 3.7\%  &  hell     &      1.9\%  &  hello    \\
 3.7\%  &  felo     &      1.2\%  &  fell     \\
 3.7\%  &  ful      &      1.2\%  &  helafelo \\
\end{tabular}
\vspace{0.2in}

@@

The next step is to build a Markov chain for a list of real words and
see what results. I built one for the SOWPODS word list, and these
are the most likely words, with real words filtered out:

% XXX improve layout
\vspace{0.2in}
\begin{tabular}{rl@{\quad\quad}rl}
0.049901545  & s     &   0.001768358  & y   \\
0.017526947  & d     &   0.001761301  & p   \\
0.009521421  & g     &   0.001653041  & a   \\
0.005506083  & c     &   0.001652864  & n   \\
0.004376836  & r     &   0.001563810  & ps  \\
0.004218223  & t     &   0.001383503  & ms  \\
0.004088377  & e     &   0.001371545  & ts  \\
0.003560976  & m     &   0.001327023  & ds  \\
0.003248559  & ss    &   0.001188715  & hy  \\
0.002001529  & rs    &   0.001166457  & k   \\
0.001958674  & h     &   0.001160619  & ng  \\
0.001873761  & l     &   0.001142785  & ly  \\
\end{tabular}
\vspace{0.2in}

Ugh, poop city! Actually, it turns out that when you see enough words,
you see enough pairs that all sorts of junk looks likely. For example,
``ng'' is easily explained by many words starting with {\it n}, {\it
g} often following {\it n}, and many words ending with {\it g}. Even
though each pair makes sense, the whole thing doesn't look like a word,
because we expect to at least see a vowel at some point, for one thing.

There is a standard solution to this problem, which is to generalize
the Markov chain to keep more than one letter of history. So instead
of just tallying how often {\it g} follows {\it n}, we count how often
{\it g} follows {\it in} (and any other pair of letters). This makes
the table pretty large, but I went through some trouble to put a
graphic in Figure~\ref{fig:sowpodstrigrams} because it looks pretty
cool.

@@

% word list from Italian Scrabble, which I bet is called
% {Scrabbizzimo!}

@@

% TODO: portmanteautally

@@

sweeeeeeeeeeeeeeeeeeet with 19 {\it e}s, which means ``Really sweet.''

``rane'' sounds too much like ``rain'', but ``sare'' has a unique pronunciation and many people seem to think it's already a word. ``cho'' is similarly easy to pronounce and spell. I propose that it be defined as ``A kind of cheese,'' so that we can really nail the new triple entendre on the classic joke.
